Pomace: a Grappa for Non-Volatile Memory

### 2012-12-11 doc/nvm2013/paper.tex
get rid of last bad apostrophe
add graphchi and magt citations

Prior work only partially explores this potentiality. GraphChi
represents a class of approaches that use windowing methods in the
irregular application space, structuring the data on secondary storage
to support filling RAM with multiple interrelated subblocks sufficient
for each of a series of phases of computation.  Such approaches are
algorithmically efficient only when each successive phase requires
access to the entire data set.  MAGT addresses this limitation by
introducing support for asynchronous computation on graphs under the
assumption that RAM is sized to accommodate data structures
proportional to vertex-count, still leaving edges on non-volatile
storage.  In addition, both methods apply only to single node systems:
Grappa provides a global view of memory on multinode systems.

@@

\paragraph{SSDs assume locality.} In our benchmarks, we find the average request size to be
less than 64 bytes. Today’s SSDs are optimized for reads in the
kilobyte range.

@@

v\subsubsection{Using future memory technologies}

>>>>

Prior work only partially explores this potentiality. GraphChi~\cite{graphchi:osdi12}
represents a class of approaches that use windowing methods in the
irregular application space, structuring the data on secondary storage
to support filling RAM with multiple interrelated subblocks sufficient
for each of a series of phases of computation.  Such approaches are
algorithmically efficient only when each successive phase requires
access to the entire data set.  MAGT~\cite{magt:2010} addresses this limitation by
introducing support for asynchronous computation on graphs under the
assumption that RAM is sized to accommodate data structures
proportional to vertex-count, still leaving edges on non-volatile
storage.  In addition, both methods apply only to single node systems:
Grappa provides a global view of memory on multinode systems.

@@

\paragraph{SSDs assume locality.} In our benchmarks, we find the average request size to be
less than 64 bytes. Today's SSDs are optimized for reads in the
kilobyte range.

@@

\subsubsection{Using future memory technologies}
